---
title: "project"
author: "chaitanya kommalapat sai panguluri " 
date: "March 31, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

question:-how the un employement rate varies in newyork from 1990 to 2019 with respective labor force and area.
source:-https://catalog.data.gov/dataset/local-area-unemployment-statistics-beginning-1976

```{r}

NewYork  <-
  read.csv("Local_Area_Unemployment_Statistics__Beginning_1976.csv")
print(NewYork )

```
The sign of a regression coefficient tells you whether there is a positive or negative correlation between each independent variable the dependent variable. A positive coefficient indicates that as the value of the independent variable increases, the mean of the dependent variable also tends to increase. A negative coefficient suggests that as the independent variable increases, the dependent variable tends to decrease.

```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)
library(cluster)

fit<-lm(formula = Unemployment.Rate~Year,data = NewYork)
fit

 a<-summary(fit)
 a

NewYork$predicted<-predict(fit)
NewYork
NewYork$residuals<-residuals(fit)
NewYork


ggplot(NewYork, aes(x = Year, y = residuals)) + geom_point()+ 
   geom_segment(aes(xend = Year, yend = 0), alpha = .2) + geom_hline(
    yintercept=0)
```

The sign of a regression coefficient tells you whether there is a positive or negative correlation between each independent variable the dependent variable. in above data year having a positive coefficient indicates that as the value of the year (independent variable increases), the mean of the  Unemployment.Rate (dependent variable )also tends to increase.
```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)
library(cluster)

fit2<-lm(formula = Unemployment.Rate~Year+Labor.Force,data = NewYork)
fit2

 b<-summary(fit2)
 b

NewYork$predicted<-predict(fit2)
NewYork
NewYork$residuals<-residuals(fit2)
NewYork


ggplot(NewYork, aes(x = Year, y = residuals)) + geom_point()+
   geom_segment(aes(xend = Year, yend = 0), alpha = .2) + geom_hline(
    yintercept=0)

```

The sign of a regression coefficient tells you whether there is a positive or negative correlation between each independent variable the dependent variable. in above data year,Labor.Force having a positive coefficient indicates that as the value of the year ,Labor.Force(independent variable increases), the mean of the  Unemployment.Rate (dependent variable )also tends to increase.
```{r}
library(rvest)
library(plyr)
library(lubridate)
library(ggplot2)
library(cluster)

fit3<-lm(formula = Unemployment.Rate~Year+Labor.Force+ factor(Area),data = NewYork)
fit3

 c<-summary(fit3)
 c

NewYork$predicted<-predict(fit3)
NewYork
NewYork$residuals<-residuals(fit3)
NewYork


ggplot(NewYork, aes(x = Year, y = residuals)) + geom_point()+
   geom_segment(aes(xend = Year, yend = 0), alpha = .2) + geom_hline(
    yintercept=0)
```
  Generally, you choose the models that have higher adjusted and predicted R-squared values. These statistics are designed to avoid a key problem with regular R-squared—it increases every time you add a predictor and can trick you into specifying an overly complex model.# from the above three models the  third model is the best model because it has highest Adjusted R-squared value.

The adjusted R squared increases only if the new term improves the model more than would be expected by chance and it can also decrease with poor quality predictors.
The predicted R-squared is a form of cross-validation and it can also decrease. Cross-validation determines how well your model generalizes to other data sets by partitioning your dataThe sign of a regression coefficient tells you .
# from the above three models the  third model is the best model because it has highest Adjusted R-squared value.

whether there is a positive or negative correlation between each independent variable the dependent variable. in above data year,Labor.Force,factor(Area), having a positive coefficient indicates that as the value of the year ,Labor.Force,factor(Area)(independent variable increases), the mean of the  Unemployment.Rate (dependent variable )also tends to increase.
